---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# runr

<!-- badges: start -->
<!-- badges: end -->

The goal of runr is to make working with running data easier. 

## Installation

You can install the development version of runr from [Github](https://github.com/christian-million/runr) with:

``` r
# install.packages("remotes")

remotes::install_github("christian-million/runr")
```

## Example

To see how I used these functions to prepare for the 2019 California International Marathon, check out [my blog posts](https://christianmillion.com/post/running/cim-2019-prep/).

```{r load}
# Load the package
library(runr)
```

Let's say I am preparing to run a marathon, and I want to see how fast I would need to run to hit my goals. First, let's set some goals:

```{r set_goals}
 # Setting Goals for Exemplary Purposes
 goal_dist <- 26.2       # Marathon distance in miles
 
 goal_pace <- "08:01"    # Pace in minutes per mile

 goal_time <- "03:30:00" # Total time in hours, minutes, and seconds.
```

```{r calc}
 calc_time(goal_dist, goal_pace) # See below section for why runr isn't perfectly precise right now.
 calc_pace(goal_dist, goal_time)
 calc_dist(goal_time, goal_pace)
```

Now that I know my goal time, let's see how long into the race I should be at during each mile.

```{r calc_splits}
 calc_splits(goal_dist, goal_time)
```

We haven't formally told any of these functions that I am counting miles and not kilometers. I'm just more used to minute-per-mile pacing. But what if I wanted to know what my marathon training stats in kilometers?

```{r km_stats}
goal_dist_km <- mi_to_km(goal_dist) # A wrapper around `convert_dist()`
  
goal_pace_km <- convert_pace(goal_pace, from = "mi", to = "km")

goal_dist_km
goal_pace_km
```

## Current State and Future Plans

Currently, `runr` is not very precise due to the amount of rounding errors. The rounding errors were a quick fix for pretty printing.
For now, this is okay, though I would eventually prefer it to be even more precise. 

Currently `runr` really only has functionality to plan theoretical runs. In the future, I am hoping
that it will work with real-world running data.

There are dependencies on `stringr` and `lubridate`. 

  - The only reason that `stringr` is a dependency is because of `stringr::str_pad`. I tried some alternatives, like `sprintf()`, but depending on my inputs I kept getting errors. I'm hoping to remove the `stringr` dependency, as it seems unnecessary. I'll keep working on a pad function that I am happy with.
  
  - I am okay with the `lubridate` dependency, even though the functions used could be replaced with base functions, because in the future I imagine there will be more need to rely on it. If not, though, I'll practice base r by creating base equivalents.

## Feedback and Issues

I'm trying to become more familiar with Github's collaboration tools, so feel free to submit an issue or pull request.

Any and all feedback is welcome.
